---
title: "Project"
output: html_document
date: "2023-04-22"
---

# Graded Response Model EFA

```{r}
library(mirt)
Data_CVI <- readxl::read_xlsx("~/Rayne/Exchange/PSYC 520/Data_CVI.xlsx")
Data_CVI$`CVI12.591_M` <- 5-Data_CVI$`CVI12.591_M`

# Dataset of Honor Facet
CVI_Ach_H <- Data_CVI[,c("CVI12.3_H","CVI12.35_H","CVI12.50_H","CVI12.213_H","CVI12.517_H","CVI12.651_H","CVI12.659_H","CVI12.664_H")]

# Dataset of Money Facet
CVI_Ach_M <- Data_CVI[,c("CVI12.55_M",	"CVI12.57_M",	"CVI12.62_M","CVI12.86_M",	"CVI12.89_M",	"CVI12.591_M")]

# Dataset of Result Facet
CVI_Ach_R <- Data_CVI[,c("CVI12.78_R",	"CVI12.79_R",	"CVI12.80_R",	"CVI12.85_R",	"CVI12.102_R",	"CVI12.103_R")]

CVI_Ach <- data.frame(c(CVI_Ach_H,CVI_Ach_M,CVI_Ach_R))
```

# Assumption Testing
Unidimensionality - RMSEA and CFI 
Local dependence - MI and Residual correlations
## Monotonicity

# Separate Model
## Honor Model
```{r}
m_grm_H <- mirt(CVI_Ach_H, 1, itemtype = "graded")
summary(m_grm_H)
plot(m_grm_H)
plot(m_grm_H, type = "info")
plot(m_grm_H, type = "trace")
coef(m_grm_H)
anova(mirt(CVI_Ach_R, 1, itemtype = "graded",constrained = TRUE),mirt(CVI_Ach_R, 1, itemtype = "graded",constrained = FALSE)) #No significant difference
```
## Result Model
```{r}
m_grm_R <- mirt(CVI_Ach_R, 1, itemtype = "graded")
summary(m_grm_R)
plot(m_grm_R)
plot(m_grm_R, type = "info")
plot(m_grm_R, type = "trace")
coef(m_grm_R)
anova(mirt(CVI_Ach_R, 1, itemtype = "graded",constrained = TRUE),mirt(CVI_Ach_R, 1, itemtype = "graded",constrained = FALSE)) #No significant difference
```
## Money Model
```{r}
m_grm_M <- mirt(CVI_Ach_M, 1, itemtype = "graded")
summary(m_grm_M)
plot(m_grm_M)
plot(m_grm_M, type = "info")
plot(m_grm_M, type = "trace")
coef(m_grm_M)
anova(mirt(CVI_Ach_M, 1, itemtype = "graded",constrained = TRUE),mirt(CVI_Ach_M, 1, itemtype = "graded",constrained = FALSE)) #No significant difference
```


# Differential Item Fucntioning
Load the Libraries
```{r}
library(tidyverse) #For data manipulation
library(tableone) # For creating tables
library(lordif) # For DIF test 
library(psych)
```

```{r}
Data_CVI <- readxl::read_xlsx("~/Rayne/Exchange/PSYC 520/Data_CVI.xlsx")
Data_CVI$`CVI12.591_M` <- 5-Data_CVI$`CVI12.591_M`

# Dataset of Honor Facet
CVI_Ach_Horg <- Data_CVI[,c("CVI12.3_H","CVI12.35_H","CVI12.50_H","CVI12.213_H","CVI12.517_H","CVI12.651_H","CVI12.659_H","CVI12.664_H","Origin")]
CVI_Ach_Horg1 <- as.data.frame(subset(CVI_Ach_Horg,(Origin =="Mainland China" | Origin =="Hong Kong"), select = c(1:8,Origin)))
# Dataset of Money Facet
CVI_Ach_Morg <- Data_CVI[,c("CVI12.55_M",	"CVI12.57_M",	"CVI12.62_M","CVI12.86_M",	"CVI12.89_M",	"CVI12.591_M","Origin")]
CVI_Ach_Morg1 <- as.data.frame(subset(CVI_Ach_Morg,(Origin =="Mainland China" | Origin =="Hong Kong"), select = c(1:6,Origin)))
# Dataset of Result Facet
CVI_Ach_Rorg <- Data_CVI[,c("CVI12.78_R",	"CVI12.79_R",	"CVI12.80_R",	"CVI12.85_R",	"CVI12.102_R",	"CVI12.103_R","Origin")]
CVI_Ach_Rorg1 <- as.data.frame(subset(CVI_Ach_Rorg,(Origin =="Mainland China" | Origin =="Hong Kong"), select = c(1:6,Origin)))
#CVI_Ach_O<-as.data.frame(subset(Data_CVI,(Origin =="Mainland China" | Origin =="Hong Kong"), select = c(4:23,Origin)))

```

## Separate Models
### lordif()
Allowing the R functions to specify the anchor items.
$\chi^2$ as detection criterion, and $R^2$ as the magnitude measure
#### Honor
```{r}
originDIF_H_Chi <- lordif(as.data.frame(CVI_Ach_Horg1[,1:8]), 
                   group = CVI_Ach_Horg1[,9],
                   model="GRM" )
originDIF_H_Chi #All items got flagged

originDIF_H_R2 <- lordif(as.data.frame(CVI_Ach_Horg1[,1:8]), 
                    group = CVI_Ach_Horg1[,9],
                    criterion=c("R2"),
                    pseudo.R2=c("McFadden"),#"Nagelkerke","CoxSnell"),
                    R2.change=0.02, 
                    model="GRM" )
originDIF_H_R2 # No item got flagged

originDIF_H_Beta <- lordif(as.data.frame(CVI_Ach_Horg1[,1:8]), 
                    group = CVI_Ach_Horg1[,9],
                    criterion="Beta",
                    beta.change = 0.1, 
                    model="GRM" )
originDIF_H_Beta # No item got flagged

```
#### Money
```{r}
originDIF_M_Chi <- lordif(as.data.frame(CVI_Ach_Morg1[,1:6]), 
                    group = CVI_Ach_Morg1[,7], 
                    model="GRM" )
originDIF_M_Chi #Items flagged: 3, 4, 6 

originDIF_M_R2 <- lordif(as.data.frame(CVI_Ach_Morg1[,1:6]), 
                    group = CVI_Ach_Morg1[,7], 
                    criterion=c("R2"),
                    pseudo.R2=c("McFadden","Nagelkerke","CoxSnell"),
                    R2.change=0.02, 
                    model="GRM" )
originDIF_M_R2 #Items flagged: 4 
par(mar = c(2, 2, 2, 2))
plot(originDIF_M_R2, labels = c('Mainland', 'Hong Kong')) 

originDIF_M_Beta <- lordif(as.data.frame(CVI_Ach_Morg1[,1:6]), 
                    group = CVI_Ach_Morg1[,7], 
                    criterion="Beta",
                    beta.change = 0.1, 
                    model="GRM" )
originDIF_M_Beta #None is flagged
```
#### Result
```{r}
originDIF_R_Chi <- lordif(as.data.frame(CVI_Ach_Rorg1[,1:6]), 
                    group = CVI_Ach_Rorg1[,7], 
                    model="GRM" )
originDIF_R_Chi #All are flagged

originDIF_R_R2 <- lordif(as.data.frame(CVI_Ach_Rorg1[,1:6]), 
                    group = CVI_Ach_Rorg1[,7],
                    criterion=c("R2"),
                    pseudo.R2=c("McFadden","Nagelkerke","CoxSnell"),
                    #alpha =0.01,
                    R2.change=0.02, 
                    model="GRM" )
originDIF_R_R2 #None is flagged

originDIF_R_Beta <- lordif(as.data.frame(CVI_Ach_Rorg1[,1:6]), 
                    group = CVI_Ach_Rorg1[,7],
                    criterion="Beta",
                    beta.change = 0.1, 
                    model="GRM" )
originDIF_R_Beta #None is flagged



```
loadif without anchor shows inconsisent results across criterion.

###DIF()
Specifying the anchor item(s) using the all-other anchor approach (AOAA) approach

Honor
```{r}
H_model<-'Honor ~= 1-6'
H_grm <- mirt.model(H_model, itemnames = 1:8)
H_mg <- multipleGroup(data = CVI_Ach_Horg1[,1:8],model = H_model,itemtype = "graded",group = as.factor(CVI_Ach_Horg1[,9]), invariance = c(colnames(CVI_Ach_Horg1[,1:8]),"free_means","free_var"))
# test uniform DIF
H_dropdown_unif <- DIF(H_mg, 'd', scheme = 'drop') #Nonsignificant
# test non-uniform DIF
H_dropdown_nonunif <- DIF(H_mg, 'a1',  scheme = 'drop') # Significant at CVI12.3_H, CVI12.50_H, CVI12.651_H
round(H_dropdown_unif,3)
round(H_dropdown_nonunif,3)
```

```{r}
# Select from the ones which are nonsignificant for DIF with the maximum slope as the anchor item: CVI12.664_H(=2.082)
H_DIF_anch <- lordif(resp.data = CVI_Ach_Horg1[,1:8],
 group = as.factor(CVI_Ach_Horg1[,9]),
 model = "GRM",
 anchor = c(7))
H_DIF_anch # Items flagged: 1, 2, 5, 6, 7, 8 

H_mg_anch <- multipleGroup(data = CVI_Ach_Horg1[,1:8],model = H_grm,itemtype = "graded",group = as.factor(CVI_Ach_Horg1[,9]),
 invariance = c('CVI12.664_H', 'free_means','free_var'))
coef(H_mg_anch, simplify=T)

# test uniform DIF
anch_unif_H <- DIF(H_mg_anch,'d',items2test = c(1:6,8))
# test non-uniform DIF
anch_nonunif_H <- DIF(H_mg_anch,'a1',items2test = c(1:6,8))
```

Money
```{r}
M_model<-'Money ~= 1-6'
M_grm <- mirt.model(M_model, itemnames = 1:6)
M_mg <- multipleGroup(data = CVI_Ach_Morg1[,1:6],model = M_model,itemtype = "graded",group = as.factor(CVI_Ach_Morg1[,7]), invariance = c(colnames(CVI_Ach_Morg1[,1:6]),"free_means","free_var"))
# test uniform DIF
M_dropdown_unif <- DIF(M_mg, 'd', scheme = 'drop') #Nonsignificant
# test non-uniform DIF
M_dropdown_nonunif <- DIF(M_mg, 'a1',  scheme = 'drop') # Significant at CVI12.62_M(p = 0.006)
round(M_dropdown_unif,3)
round(M_dropdown_nonunif,3)
```
Anchor Approach
```{r}
# All items here are not statistically significant for both types of DIF.
# Select the ones with the maximum slope as the anchor item: CVI12.80_R
M_DIF_anch <- lordif(resp.data = CVI_Ach_Morg1[,1:6],
 group = as.factor(CVI_Ach_Morg1[,7]),
 
 model = "GRM",
 anchor = c(1))
M_DIF_anch

M_mg_anch <- multipleGroup(data = CVI_Ach_Morg1[,1:6],model = M_grm,itemtype = "graded",group = as.factor(CVI_Ach_Morg1[,7]),
 invariance = c('CVI12.55_M', 'free_means','free_var'))
coef(M_mg_anch, simplify=T)

# test uniform DIF
anch_unif_M <- DIF(M_mg_anch,'d',items2test = 2:6, scheme = 'drop')
# test non-uniform DIF
anch_nonunif_M <- DIF(M_mg_anch,'a1', items2test = 2:6,, scheme = 'drop')

round(anch_unif_M,3)
round(anch_nonunif_M,3)
```


