---
title: "Project"
output: html_document
date: "2023-04-22"
---

# Package and Data loading

```{r}
library(mirt)
Data_CVI <- readxl::read_xlsx("~/Rayne/Exchange/PSYC 520/Data_CVI.xlsx")
Data_CVI$`CVI12.591_M` <- 5-Data_CVI$`CVI12.591_M`

# Dataset of Honor Facet
CVI_Ach_H <- Data_CVI[,c("CVI12.3_H","CVI12.35_H","CVI12.50_H","CVI12.213_H","CVI12.517_H","CVI12.651_H","CVI12.659_H","CVI12.664_H")]

# Dataset of Money Facet
CVI_Ach_M <- Data_CVI[,c("CVI12.55_M",	"CVI12.57_M",	"CVI12.62_M","CVI12.86_M",	"CVI12.89_M",	"CVI12.591_M")]

# Dataset of Result Facet
CVI_Ach_R <- Data_CVI[,c("CVI12.78_R",	"CVI12.79_R",	"CVI12.80_R",	"CVI12.85_R",	"CVI12.102_R",	"CVI12.103_R")]

CVI_Ach <- data.frame(c(CVI_Ach_H,CVI_Ach_M,CVI_Ach_R))
CVI_Ach_O <- data.frame(c(CVI_Ach_H,CVI_Ach_M,CVI_Ach_R,Data_CVI$"Origin"))
```

```{r}
# Dataset of Honor Facet
CVI_Ach_Horg <- Data_CVI[,c("CVI12.3_H","CVI12.35_H","CVI12.50_H","CVI12.213_H","CVI12.517_H","CVI12.651_H","CVI12.659_H","CVI12.664_H","Origin")]
CVI_Ach_Horg1 <- as.data.frame(subset(CVI_Ach_Horg,(Origin =="Mainland China" | Origin =="Hong Kong"), select = c(1:8,Origin)))
# Dataset of Money Facet
CVI_Ach_Morg <- Data_CVI[,c("CVI12.55_M",	"CVI12.57_M",	"CVI12.62_M","CVI12.86_M",	"CVI12.89_M",	"CVI12.591_M","Origin")]
CVI_Ach_Morg1 <- as.data.frame(subset(CVI_Ach_Morg,(Origin =="Mainland China" | Origin =="Hong Kong"), select = c(1:6,Origin)))
# Dataset of Result Facet
CVI_Ach_Rorg <- Data_CVI[,c("CVI12.78_R",	"CVI12.79_R",	"CVI12.80_R",	"CVI12.85_R",	"CVI12.102_R",	"CVI12.103_R","Origin")]
CVI_Ach_Rorg1 <- as.data.frame(subset(CVI_Ach_Rorg,(Origin =="Mainland China" | Origin =="Hong Kong"), select = c(1:6,Origin)))
#CVI_Ach_O<-as.data.frame(subset(Data_CVI,(Origin =="Mainland China" | Origin =="Hong Kong"), select = c(4:23,Origin)))

```

```{r}
# Produce descriptive/distribution of the items
tha_data_inuse <- Data_CVI %>% mutate(across(.cols = c("CVI12.3_H","CVI12.35_H","CVI12.50_H","CVI12.213_H","CVI12.517_H","CVI12.651_H","CVI12.659_H","CVI12.664_H","CVI12.55_M",	"CVI12.57_M",	"CVI12.62_M","CVI12.86_M",	"CVI12.89_M",	"CVI12.591_M","CVI12.78_R",	"CVI12.79_R",	"CVI12.80_R",	"CVI12.85_R",	"CVI12.102_R",	"CVI12.103_R","Origin"),factor))
tabFirst <- CreateTableOne(vars = c("CVI12.3_H","CVI12.35_H","CVI12.50_H","CVI12.213_H","CVI12.517_H","CVI12.651_H","CVI12.659_H","CVI12.664_H","CVI12.55_M",	"CVI12.57_M",	"CVI12.62_M","CVI12.86_M",	"CVI12.89_M",	"CVI12.591_M","CVI12.78_R",	"CVI12.79_R",	"CVI12.80_R",	"CVI12.85_R",	"CVI12.102_R",	"CVI12.103_R","Origin"), data = tha_data_inuse,
includeNA = T,test = F)
tabFirst
```

```{r}
# Exploratory
CVI_Ach <- data.frame(CVI_Ach_H,CVI_Ach_M,CVI_Ach_R)
m_grm_1 <- mirt(CVI_Ach, 1, itemtype = "graded")

## 2-Factor Model
m_grm_2 <- mirt(CVI_Ach, 2, itemtype = "graded")
anova(m_grm_1,m_grm_2) # Compare model fit between 1-factor and 2-factor model

## 3-Factor Model
m_grm_3 <- mirt(CVI_Ach, 3, itemtype = "graded")
anova(m_grm_2,m_grm_3)

```

# Assumption Testing

## Unidimensionality
Scree plot of eigenvalue
```{r}
polycorr_H <- polychoric(CVI_Ach_H,global=FALSE)$rho
poly_eigen_H <- eigen(polycorr_H)$values
round(poly_eigen_H,3)
plot(1:length(poly_eigen_H),poly_eigen_H, type="b", pch=20, xlab="",ylab="Eigenvalues")

polycorr_M <- polychoric(CVI_Ach_M,global=FALSE)$rho
poly_eigen_M <- eigen(polycorr_M)$values
round(poly_eigen_M,3)
plot(1:length(poly_eigen_M),poly_eigen_M, type="b", pch=20, xlab="",ylab="Eigenvalues")

polycorr_R <- polychoric(CVI_Ach_R,global=FALSE)$rho
poly_eigen_R <- eigen(polycorr_R)$values
round(poly_eigen_R,3)
plot(1:length(poly_eigen_R),poly_eigen_R, type="b", pch=20, xlab="",ylab="Eigenvalues")
```


## Local dependence - Residual correlations
```{r}
m_grm_H <- mirt(CVI_Ach_H, 1, itemtype = "graded")
round(M2(m_grm_H, residmat = TRUE),3)
m_grm_M <- mirt(CVI_Ach_M, 1, itemtype = "graded")
round(M2(m_grm_M, residmat = TRUE),3)
m_grm_R <- mirt(CVI_Ach_R, 1, itemtype = "graded")
round(M2(m_grm_R, residmat = TRUE),3)
```

## Monotonicity

```{r}
library(mokken)
H.monot<-summary(check.monotonicity(CVI_Ach_H, minvi = 0.03) )
H.monot
M.monot<-summary(check.monotonicity(CVI_Ach_M, minvi = 0.03) )
M.monot
R.monot<-summary(check.monotonicity(CVI_Ach_R, minvi = 0.03) )
R.monot
```

# Separate Model
## Honor Model

```{r}
m_grm_H <- mirt(CVI_Ach_H, 1, itemtype = "graded")
summary(m_grm_H)
plot(m_grm_H)
plot(m_grm_H, type = "info")
plot(m_grm_H, type = "infotrace")
plot(m_grm_H, type = "trace")
Theta <- matrix(seq(-6,6,length.out = 200))
# expected.H <- expected.item(extract.item(m_grm_H,item = 1),Theta,min(CVI_Ach_H[,1]))
plot(data.frame(expected.H,Theta= Theta))
coef(m_grm_H)
# Compare constrained and non-contrained model
anova(mirt(CVI_Ach_R, 1, itemtype = "graded",constrained = TRUE),mirt(CVI_Ach_R, 1, itemtype = "graded",constrained = FALSE)) #No significant difference
M2(m_grm_H)
```


## Money Model

```{r}
m_grm_M <- mirt(CVI_Ach_M, 1, itemtype = "graded")
summary(m_grm_M)
plot(m_grm_M)
plot(m_grm_M, type = "info")
plot(m_grm_H, type = "infotrace")
plot(m_grm_M, type = "trace")
coef(m_grm_M)
anova(mirt(CVI_Ach_M, 1, itemtype = "graded",constrained = TRUE),mirt(CVI_Ach_M, 1, itemtype = "graded",constrained = FALSE)) #No significant difference

```

## Result Model

```{r}
m_grm_R <- mirt(CVI_Ach_R, 1, itemtype = "graded")
summary(m_grm_R)
plot(m_grm_R)
plot(m_grm_R, type = "info")
plot(m_grm_R, type = "infotrace")
plot(m_grm_R, type = "trace")
coef(m_grm_R)
anova(mirt(CVI_Ach_R, 1, itemtype = "graded",constrained = TRUE),mirt(CVI_Ach_R, 1, itemtype = "graded",constrained = FALSE))#No significant difference

```

# Differential Item Fucntioning

Load the Libraries

```{r}
library(tidyverse) 
library(tableone) 
library(lordif) # For DIF test 
library(psych)
```


## Separate Models

### lordif()
#### Honor
Allowing the R functions to specify the anchor items. $\chi^2$ as detection criterion, and $R^2$ as the magnitude measure chisq1,2 -- uniform DIF chisq1,3 -- nonuniform DIF chisq2,3 -- total DIF \#### Honor

```{r}
originDIF_H_Chi <- lordif(as.data.frame(CVI_Ach_Horg1[,1:8]), 
                   group = CVI_Ach_Horg1[,9],
                   alpha = 0.01,
                   model="GRM" )
originDIF_H_Chi #All items got flagged

originDIF_H_R2 <- lordif(as.data.frame(CVI_Ach_Horg1[,1:8]), 
                    group = CVI_Ach_Horg1[,9],
                    criterion=c("R2"),
                    pseudo.R2=c("McFadden"),#"Nagelkerke","CoxSnell"),
                    R2.change=0.02, 
                    model="GRM" )
originDIF_H_R2 # No item got flagged

originDIF_H_Beta <- lordif(as.data.frame(CVI_Ach_Horg1[,1:8]), 
                    group = CVI_Ach_Horg1[,9],
                    criterion="Beta",
                    beta.change = 0.1, 
                    model="GRM" )
originDIF_H_Beta # No item got flagged

```

Set I3 is selected as the anchor item, since it is the closest to the selection criteria of alpha = 0.01 when using chisq as the selection rule.

```{r}
H_DIF_anch <- lordif(resp.data = CVI_Ach_Horg1[,1:8],
 group = as.factor(CVI_Ach_Horg1[,9]),
 model = "GRM",
 anchor = c(3))
H_DIF_anch # Items flagged: 1, 2, 5, 6, 7, 8 
```

#### Money

```{r}
originDIF_M_Chi <- lordif(as.data.frame(CVI_Ach_Morg1[,1:6]), 
                    group = CVI_Ach_Morg1[,7], 
                    model="GRM" )
originDIF_M_Chi #Items flagged: 3, 4, 6 
plot(originDIF_M_Chi, labels = c('Mainland', 'Hong Kong')) 

originDIF_M_R2 <- lordif(as.data.frame(CVI_Ach_Morg1[,1:6]), 
                    group = CVI_Ach_Morg1[,7], 
                    criterion=c("R2"),
                    pseudo.R2=c("McFadden","Nagelkerke","CoxSnell"),
                    R2.change=0.02, 
                    model="GRM" )
originDIF_M_R2 #Items flagged: 4 
plot(originDIF_M_R2, labels = c('Mainland', 'Hong Kong')) 

originDIF_M_Beta <- lordif(as.data.frame(CVI_Ach_Morg1[,1:6]), 
                    group = CVI_Ach_Morg1[,7], 
                    criterion="Beta",
                    beta.change = 0.1, 
                    model="GRM" )
originDIF_M_Beta #None is flagged
```

I1, I2, I5 is selected as the anchor item, since it is nonsignificant to the selection criteria of alpha = 0.01 when using chisq as the selection rule, and has the largest slope.

Anchor item: I1, I2, I5

```{r}
M_DIF_anch <- lordif(resp.data = CVI_Ach_Morg1[,1:6],
 group = as.factor(CVI_Ach_Morg1[,7]),
 model = "GRM",
 anchor = c(1,2,5))
M_DIF_anch # Items flagged: 3, 4, 6 
```

#### Result

```{r}
originDIF_R_Chi <- lordif(as.data.frame(CVI_Ach_Rorg1[,1:6]), 
                    group = CVI_Ach_Rorg1[,7], 
                    model="GRM" )
originDIF_R_Chi #All are flagged

originDIF_R_R2 <- lordif(as.data.frame(CVI_Ach_Rorg1[,1:6]), 
                    group = CVI_Ach_Rorg1[,7],
                    criterion=c("R2"),
                    pseudo.R2=c("McFadden","Nagelkerke","CoxSnell"),
                    #alpha =0.01,
                    R2.change=0.02, 
                    model="GRM" )
originDIF_R_R2 #None is flagged

originDIF_R_Beta <- lordif(as.data.frame(CVI_Ach_Rorg1[,1:6]), 
                    group = CVI_Ach_Rorg1[,7],
                    criterion="Beta",
                    beta.change = 0.1, 
                    model="GRM" )
originDIF_R_Beta #None is flagged

```

